\section{Build and Deployment}
\label{sec:build-and-deployment}

Each of the components of the dashboard has a separate Dockerfile, which allows us to containerize the application. Some of the scanners, which do not have a publicly available Docker image, have to be containerized separately. For instance, we build Prowler on a Python base as shown on the Listing~\ref{lst:prowler-dockerfile}.

\begin{lstlisting}[language=Dockerfile, caption={[Dockerfile definition of Prowler image] Dockerfile definition of Prowler image.}, label={lst:prowler-dockerfile}]
    FROM python:3.12-slim

    RUN pip install prowler
    
    CMD ["prowler"]    
\end{lstlisting}

In order to make it easier to build different components of the application, we define a Bash script that does all of the work for us. 

Deployment of the whole application is done via the Helm Chart. It defines all of the Kubernetes resources for the application that are deployed inside the cluster. The deployment can be configured using \lstinline{values.yaml} file, that defines the Helm values, which are then substituted into the Helm templates. Installation is done with 
\begin{center}
    \lstinline{helm -n ksa upgrade --install ksa .}
\end{center} 
command, that creates Deployments, StatefulSet, Services and PVCs. There are also \lstinline{reinstall.sh} and \lstinline{redeploy.sh} Bash scripts defined to automate the installation and redeployment processes, respectively. Listing~\ref{lst:ksa-kubernetes-resources} shows the workloads created by the Helm chart and the Jobs created by the dashboard itself.

\begin{lstlisting}[language=CustomBash, caption={[Kubernetes workloads for the KSA Dashboard] Kubernetes workloads for the KSA Dashboard.}, label={lst:ksa-kubernetes-resources}]
$ k get deployments,sts,jobs,pods

NAME                           READY UP-TO-DATE AVAILABLE AGE
deployment.apps/ksa-aggregator 1/1   1          1         2d21h
deployment.apps/ksa-dashboard  1/1   1          1         2d21h
deployment.apps/ksa-parser     1/1   1          1         2d21h

NAME                      READY AGE
statefulset.apps/postgres 1/1   2d21h

NAME                        STATUS   COMPLETIONS DURATION AGE
job.batch/kube-bench-runner Complete 1/1         44s      2d21h
job.batch/prowler-runner    Complete 1/1         4s       2d21h
job.batch/trivy-runner      Complete 1/1         3m20s    2d11h

NAME                                READY STATUS    RESTARTS AGE
pod/ksa-aggregator-7d79b846d5-xzpgt 1/1   Running   0        2d21h
pod/ksa-dashboard-5bd4767cdd-q7ksg  1/1   Running   0        2d21h
pod/ksa-parser-79b55cdf7d-npdjp     1/1   Running   0        2d21h
pod/kube-bench-runner-948bd         0/1   Completed 0        2d21h
pod/postgres-0                      1/1   Running   0        2d21h
pod/prowler-runner-rpdn4            0/1   Completed 0        2d21h
pod/trivy-runner-qp5dw              0/1   Completed 0        2d11h
\end{lstlisting}